### 2014-11-02 simulation.Rmd
.

## Result of fitting operation
```{r, echo=FALSE}
cat("convergence: ", model@results$convergence,
    "\nmessage: ", model@results$message,
    "\n" )
```

@@

>>>>

## Result of fitting operation
```{r, echo=FALSE}
if (class(model)=="context") {
    cat("convergence: ", model@results$convergence,
        "\nmessage: ", model@results$message,
        "\n" )
} else if (class(model)=="contextMCMC") {
    cat(
        "number of batches: ", model@results$nbatch,
        "\nbatch length: ", model@results$blen,
        "\nacceptance rate: ", model@results$accept,
        "\nrun time: ", model@results$time['elapsed'],
        "\n" )
}
```

@@

# Pairwise marginal posteriors from MCMC, colored by time in MCMC run
```{r, results="asis", echo=FALSE, fig.align='center', }
if (class(model)=="contextMCMC") {
    subseq <- seq(1,nrow(model@results$batch),length.out=min(1000,nrow(model@results$batch)))
    x <- rbind( model@results$batch[subseq,], mr_compare$simulated[model@results$use.par] ) 
    colnames(x) <- rownames(mr_compare)[model@results$use.par]
    # color by time
    cols <- c( adjustcolor(rainbow(64),.2)[1+floor(65*(1:(nrow(x)-1))/nrow(x))], adjustcolor("black",.5) )
    pairs( x, col=cols, pch=20, cex=c(rep(.5,nrow(x)-1),2) )
} else {
    cat("Not an MCMC run.")
}
```
